%-------------------------
% Resume in Latex
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}


% Set the margins
\geometry{left=0.85cm, top=0.8cm, right=0.85cm, bottom=0.8cm}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]


%-------------------------
% Custom commands

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{-3mm}{#1}:\hspace{1mm} & \hspace*{0pt}\hfill{\footnotesize{ #3}} \vspace{-0.5mm}\\ \hspace{-2.9mm}#2 
    \end{tabular*}
    \vspace{0mm}
}

\newcommand{\resumeExp}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-1.2mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{\textit{#4}}
    \end{tabular*}
    \vspace{-6.1mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-1mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-6.5mm}
}

\newcommand{\resumeEdu}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.3mm} \small\textbf{#1} & \footnotesize{#3}\vspace{-1mm} \\
        \hspace{-4.3mm} \footnotesize{#2} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-3.2mm}
}

\newcommand{\resumeAchieve}[3]
{
\hspace{-3.1mm}\textbf{ #1} & {#2} & \hspace{3mm}\footnotesize{#3}
\vspace{0mm}\\
}


\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=-1.5mm]}

\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{1.5mm}}

\renewcommand{\arraystretch}{1}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------



%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%

\newcommand{\name}{Mikhail Skobov}
\newcommand{\phone}{952.220.6785}
\newcommand{\emaila}{skobovm@gmail.com}
\newcommand{\github}{kail}
\newcommand{\website}{https://skobovm.com}
\newcommand{\linkedin}{skobovm}



\begin{document}
\fontfamily{cmr}\selectfont


%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{\name}}
\end{center}
\vspace{-3.5mm}
\begin{center}
    \small{\href{https://github.com/\github}{\faGithub \hspace{0.2mm} github.com/\github} |  \href{https://www.linkedin.com/in/\linkedin/}{\faLinkedinSquare \hspace{0.2mm} linkedin.com/in/\linkedin} | \href{mailto:\emaila}{\faSend \hspace{0.2mm} \emaila} | \faPhone \hspace{0.2mm} \phone }
\end{center}
\vspace{-3mm}

%-----------EXPERIENCE-----------------
\section{Work Experience}
\resumeSubHeadingListStart

\resumeExp
{Lyft - Bikes and Scooters}
{Staff Firmware Engineer}
{November 2020 - Current}
{C, C++, Bazel}
\resumeItemListStart
\item[$\bullet$] Engineering lead for a docking stations program; managing a small team, providing technical mentorship, and driving the firmware architecture and general technical direction for the program.
\item[$\bullet$] Designed a networking architecture, with cross-functional partners, focusing on improving power consumption in LTE-based devices. This involved gaining a deep understanding of LTE architecture at the physical layer, optimizing the networking transport layer configuration, and working directly with the mobile provider for further tuning and diagnostics. 
\item[$\bullet$] Core contributor to, and maintainer of, the firmware team's embedded platform, which nearly all embedded projects at Lyft are based on. This platform provides common libraries, drivers, design patterns, and a build system which greatly improves the org's productivity.
\item[$\bullet$] Built and shipped Lyft's newest rideable, which received a \href{https://time.com/collection/best-inventions-2021/6113140/lyft-new-e-bike/b}{\textbf{TIME's Best Inventions of 2021 Award \footnotesize\faExternalLink}}. My contributions were focused on: UX (display, audio, lights, etc.), GPS, internal storage, faults, and backend communications.
\resumeItemListEnd

\resumeExp
{Lyft - Transit}
{Senior Software Engineer}
{October 2018 - November 2020}
{Go, Python, C++, Kafka}
\resumeItemListStart
\item[$\bullet$] Developed a high performance, highly-available multimodal routing engine. This was able to provide optimal route results for transit itineraries, but also allowed different modes such as walking, biking, and cars.
\item[$\bullet$] Helped grow the transit team from a startup (within Lyft) to a large engineering team; lead initiatives to improve the architecture, specifically focusing on reliability, fault-tolerance, and developer tooling.
\item[$\bullet$] Built an agent-based solution for ingesting real-time transit data, which greatly improved realtime routing results and saved Lyft \$100K annually, relative to the legacy solution.
\resumeItemListEnd


\resumeExp
{Pioneer Square Labs - AdLightning}
{Senior Software Engineer}
{June 2017 - October 2018}
{Python, Javascript, AdTech}
\resumeItemListStart
\item[$\bullet$] Designed \& built the market-leading malicious advertisement blocking platform for publishers. This protects millions of users from forced redirects and malware.
\item[$\bullet$] Implemented a large-scale, microservice-based system for markup processing that is currently handling >40MM daily ad content reports.
\item[$\bullet$] Implemented a locality-sensitive hashing algorithm for ad content similarity detection, which greatly helps reduce costs by omitting creatives which have already been processed.
\item[$\bullet$] Drove the design and architecture on our programmatic video advertisement analysis tool.
\item[$\bullet$] Contributed to the UI and back-end service for the main publisher interface.
\resumeItemListEnd


\resumeExp
{Microsoft – Interact Next}
{SDE II}
{Feb 2016 - June 2017}
{C++, C\#, Interaction Design, Accessibility}
\resumeItemListStart
\item[$\bullet$] Developed numerous features for the user-facing component of the Surface Dial.
\item[$\bullet$] Created compelling prototypes for ambient, multi-user, and/or multi-device interactions and worked with partner teams to incorporate these experiences into their products.
\item[$\bullet$] Designed and fabricated hardware development boards for evaluating user interactions with physical concept devices.
\item[$\bullet$] Built concepts for wearables, and accessories to the Windows ecosystem.
\resumeItemListEnd


\resumeExp
{Microsoft – LLILUM}
{SDE II}
{June 2015 - Feb 2016}
{C, C++, Assembly, LLVM}
\resumeItemListStart
\item[$\bullet$] Implemented drivers for low-level communication protocols (SPI, I2C, Serial, etc.).
\item[$\bullet$] Designed the middle-tier interface between C code and the managed-language interface created by LLVM.
\item[$\bullet$] Created and maintained the Visual Studio-based SDK for the platform, and was responsible for overall user experience.
\item[$\bullet$] Ported the light-weight IP stack and numerous other libraries for use from C\# on an embedded platform.
\resumeItemListEnd


\resumeExp
{Microsoft – Web Platform}
{SDE}
{August 2014 - June 2015}
{C++, Win32, UWP}
\resumeItemListStart
\item[$\bullet$] Developed and maintained features that involved mouse, touch, or keyboard input.
\item[$\bullet$] Built the infrastructure/core for the native date-time input control (<input type=”date”>).
\item[$\bullet$] Implemented Drag and Drop using new WinRT APIs, and developed cross-WWA drag support.
\item[$\bullet$] Contributed to portions of the Javascript runtime and tested against W3C specifications.
\item[$\bullet$] Shipped the first version of the Edge browser on Windows 10.
\resumeItemListEnd

\pagebreak

\resumeExp
{Microsoft – SQL, Azure}
{Intern}
{Summer 2022, 2023}
{C\#, SQL, Azure}
\resumeItemListStart
\item[$\bullet$] Developed a data-generation tool for testing the MDS feature of SQL.
\item[$\bullet$] Created test plans and wrote automated tests as part of complete feature ownership.
\item[$\bullet$] Worked on debugging stored procedures through SQL Server Management Studio.
\item[$\bullet$] Created a secure phone application for notifying developers of build and live errors.
\resumeItemListEnd


\resumeExp
{Maverick Software – Thomson Reuters}
{SDET Consultant}
{May 2010 - May 2013}
{C\#, Java, Javascript, Accesibility}
\resumeItemListStart
\item[$\bullet$] Developed web applications using C\# and ASP.NET, and created Selenium functional tests.
\item[$\bullet$] Worked on 508 Compliance trackers to provide accessibility features for the visually-impaired.
\item[$\bullet$] Rewrote components of a web application from ASP to ASP.NET.
\item[$\bullet$] Worked with large quantities of data for document retrieval/presentation services.
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5.5mm}

%-----------EDUCATION-----------------

\vspace{-2.5mm}
\section{Education}
\resumeSubHeadingListStart

\resumeProject
{University of Washington}
{M.S. Computer Science} %Project Name, Location Name
{March 2017 - May 2020} %Event Dates
{} 
\resumeItemListStart
\item[$\bullet$] Programming Systems: theory of P.S. for modern languages and architectures
\item[$\bullet$] Machine Learning: theory and impl. of decision trees, neural nets, SVM, clustering, and others
\item[$\bullet$] Entrepreneurship: built a tech startup from the ground up; pitched to VCs in the industry
\item[$\bullet$] Natural language processing, cryptography, advanced algorithms, and others. 
\resumeItemListEnd

\resumeProject
{University of Washington}
{Certificate: Embedded \& Real-Time Systems Programming} %Project Name, Location Name
{Oct. 2016 - May 2017} %Event Dates
{} 
\resumeItemListStart
\resumeItemListEnd
\vspace{-3.2mm}

\resumeProject
{University of Wisconsin - Madison}
{B.S. Computer Science} %Project Name, Location Name
{Sept. 2010 - May 2014} %Event Dates
{} 
\resumeItemListStart
\item[$\bullet$] Computer Engineering: Embedded Systems Emphasis
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-6.2mm}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProject
{Personal Monorepo \raisebox{-0.3mm}{\href{https://github.com/kail/monorepo}{\footnotesize\faExternalLink}}}{}{}{}
\vspace{-3.5mm}
\resumeItemListStart
\item[$\bullet$] Single repo containing all of the things I enjoy dabbling with
\item[$\bullet$] Terraform-based infra configuration, with simple, containerized microservices; optimized for simplicity
\item[$\bullet$] Firmware source and hardware design files for embedded projects

\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-5.5mm}

% This section is currently unused
\iffalse

\section{Technical Skills}
\vspace{0.2mm}

\small{\begin{tabular*}{\textwidth}[t]{p{0.5\textwidth} p{0.5\textwidth}}

\hspace{-3.1mm}{\textbf{ Programming languages:} C++, C, Python, C\#, Java} & {\textbf{Web Technologies:} HTML, CSS, Django, Flask, JavaScript} \\  
\hspace{-3.1mm}{\textbf{ ML/AI:} Pytorch, Numpy, Pandas, Matplotlib} & {\textbf{Miscellaneous:} MySQL, AWS, Git, Shell, Latex, Unity}
\end{tabular*}}

\vspace{-2.5mm}
\fi


\section{Patents}
\vspace{0.2mm}

\small{\begin{tabular*}{\textwidth}[t]{p{\textwidth}}
\textbf{ U.S. Patent 16/805,135: }{Transition of navigation modes for multi-modal transportation}\\
\textbf{ U.S. Patent 16/836,141: }{Multi-modal route generation system}\\
\textbf{ U.S. Patent 15/610,432: }{System and method for directed analysis of content using artifical intelligence for storage and recall}\\
\textbf{ U.S. Patent 15/397,238: }{Disambiguation of target devices using ambient signal data}\\
\end{tabular*}}

% This section is currently unused
\iffalse
\section{Achievements}
\vspace{0.2mm}
\small{\begin{tabular*}{\textwidth}[t]{p{0.22\textwidth} p{0.68\textwidth}@{\extracolsep{\fill}}r}

\resumeAchieve{Achivement 1}{Description}{2022}
\resumeAchieve{Achivement 2}{Description}{2022}

\end{tabular*}}

\vspace{-2.5mm}
\fi

%-------------------------------------------
\end{document}
